---
title: "2017 Repair dental restorations"
output:
  html_notebook:
    fig_caption: yes
    toc: yes
    toc_float: yes
  html_document:
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

Data extracted was tabulated in a google sheet. Then exported as csv file and imported in R (R Core Team (2017). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.)

Data cleaning and organization was done with package tidyverse (Hadley Wickham (2017). tidyverse: Easily Install and Load the 'Tidyverse'. R package version 1.2.1.   https://CRAN.R-project.org/package=tidyverse).

The package meta (Guido Schwarzer (2007), meta: An R package for meta-analysis, R News, 7(3), 40-45.) was used for the meta-analysis. A funnel plot was used to detect publication bias. The heterogenicity between studies was checked with I2 and visualized with a Baujat plot (Baujat B, Mahé C, Pignon JP, Hill C (2002), A graphical method for exploring heterogeneity in meta-analyses: Application to a meta-analysis of 65 trials. Statistics in Medicine, 30, 2641–2652.).  We grouped the studies with same intervention and control and considered any adverse outcome. A random effect meta-analysis using odds-ratio as outcome was performed with a Mantel-Haenzel method. A forest plot was used to visualize the overall effect of the interventions, with a 95% confidence interval.





# Paquetes
```{r, include = F, echo = F}
Packages <- c("tidyverse", "broom", "meta")
lapply(Packages, library, character.only = TRUE)
rm(Packages)
```




# Dataset

```{r}

df <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRSKuBlcQTVJK2fZyZ4Nvf4SwSqVrxcfAGhNhl6dWHU9W39oppE4Pl4lcPy-0CRGRTqQQ0IHwFgfrY8/pub?gid=0&single=true&output=csv")
```

## Data cleaning
```{r}
glimpse(df)
```
Clean dataset from empty rows, strange symbols, etc
```{r}

df <- df %>% filter(str_detect(df$Comparison, "vs"), 
                      trimws(EvA) != "", 
                    !str_detect(EvA, "\\?"), 
                    !str_detect(EvA, "%") )

df$firstAuthor <- str_trim(df$firstAuthor, "right")



```
Select only relevant columns
```{r}
df <- df %>% select(Comparison:Outcome) %>% 
  select(-quality)
```

create a new column id

```{r}
df <-  mutate(df, id = paste(firstAuthor, ", ", year, paper))

```

## Dataset clean
Converting factors to numeric variables

```{r}
glimpse(df)

df$EvA <- as.integer(df$EvA)
df$TotalA <- as.integer(df$TotalA)
df$EvB <- as.integer(df$EvB)
df$TotalB <- as.integer(df$TotalB)

df <- df %>% 
  mutate(groups = paste(Comparison, Outcome))

```
```{r}
summary(df)

```
Create groups for comparisons

Any intervention (Sealant, Refinishing or Repair) vs grouped comparison and grouped outcome
```{r}
df <- mutate(df, groups = paste( intervention_b, Outcome))
table(df$groups)
```


# 1.  No-treatment MA (6)
## Data selection
```{r}
data_meta <- df %>% 
  filter(groups == "No-treatment MA")
```
```{r}
meta1 <- metabin(EvA, TotalA, 
                 EvB, TotalB, 
                 data = data_meta,  
                 sm = "OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = paste(firstAuthor, year, intervention_a))

```


## Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE)
```


## Heterogeneity

```{r}

baujat.meta(meta1, 
            yscale = 10, xmin = 3, ymin = 10, 
            cex.studlab = .50)
```


## Meta-analysis and forest plot
```{r}
summary(meta1)
```

```{r}
meta1
```
## Forest

```{r}

forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or ref.", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No treatment",
       col.label.right    = "darkred")

```

## Export

```{r}
png(filename = "1.png", 
    type = "cairo",
    units = "in", 
    width = 10, 
    height = 5, 
    pointsize = 12, 
    res = 96)


forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or ref.", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No treatment",
       col.label.right    = "darkred")

dev.off()
```

-------------------------------------------------------------------------------


# 2. No-treatment SC (6)
## Data selection
```{r}
data_meta <- df %>% 
  filter(groups == "No-treatment SC")
data_meta
```
```{r}
meta1 <- metabin(EvA, TotalA, 
                 EvB, TotalB, 
                 data = data_meta,  
                 sm = "OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = paste(firstAuthor, year, intervention_a))

```


## Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE, 
            cex.studlab = .55)
```


## Heterogeneity

```{r}

baujat.meta(meta1, 
            yscale = 10, xmin = 3, ymin = 10, 
            cex.studlab = .50)
```


## Meta-analysis and forest plot
```{r}
summary(meta1)
```

```{r}
meta1
```
## Forest
```{r}

forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or refinishing", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No treatment",
       col.label.right    = "darkred")

```

## Export
```{r}
png(filename = "2.png", 
    type = "cairo",
    units = "in", 
    width = 10, 
    height = 5, 
    pointsize = 12, 
    res = 96)


forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or refinishing", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No treatment",
       col.label.right    = "darkred")

dev.off()

```




-------------------------------------------------------------------------------



# 3. No-treatment TS (3)
## Data selection
```{r}
data_meta <- df %>% 
  filter(groups == "No-treatment TS")
data_meta
```
```{r}
meta1 <- metabin(EvA, TotalA, 
                 EvB, TotalB, 
                 data = data_meta,  
                 sm = "OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = paste(firstAuthor, year, intervention_a))

```


## Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE, 
            cex.studlab = .55)
```


## Heterogeneity

```{r}

baujat.meta(meta1, 
            yscale = 10, xmin = 3, ymin = 10, 
            cex.studlab = .50)
```


## Meta-analysis and forest plot
```{r}
summary(meta1)
```

```{r}
meta1
```
## Forest
```{r}

forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or refinish", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No treatment",
       col.label.right    = "darkred")

```

## Export
```{r}
png(filename = "3.png", 
    type = "cairo",
    units = "in", 
    width = 10, 
    height = 5, 
    pointsize = 12, 
    res = 96)


forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or refinish", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No treatment",
       col.label.right    = "darkred")

dev.off()

```



-------------------------------------------------------------------------------

# 4. Replacement MA (5)
## Data selection
```{r}
data_meta <- df %>% 
  filter(groups == "Replacement MA")
data_meta
```
```{r}
meta1 <- metabin(EvA, TotalA, 
                 EvB, TotalB, 
                 data = data_meta,  
                 sm = "OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = paste(firstAuthor, year, intervention_a))

```


## Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE, 
            cex.studlab = .55)
```


## Heterogeneity

```{r}

baujat.meta(meta1, 
            yscale = 10, xmin = 3, ymin = 10, 
            cex.studlab = .50)
```


## Meta-analysis and forest plot
```{r}
summary(meta1)
```

```{r}
meta1
```
## Forest
```{r}

forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or repair", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Replacement",
       col.label.right    = "darkred")

```


## Export
```{r}
png(filename = "4.png", 
    type = "cairo",
    units = "in", 
    width = 10, 
    height = 5, 
    pointsize = 12, 
    res = 96)


forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or repair", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Replacement",
       col.label.right    = "darkred")

dev.off()

```

-------------------------------------------------------------------------------

# 5. Replacement SC (5)
## Data selection
```{r}
data_meta <- df %>% 
  filter(groups == "Replacement SC")
data_meta
```
```{r}
meta1 <- metabin(EvA, TotalA, 
                 EvB, TotalB, 
                 data = data_meta,  
                 sm = "OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = paste(firstAuthor, year, intervention_a))

```


## Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE, 
            cex.studlab = .55)
```


## Heterogeneity

```{r}

baujat.meta(meta1, 
            yscale = 10, xmin = 3, ymin = 10, 
            cex.studlab = .50)
```


## Meta-analysis and forest plot
```{r}
summary(meta1)
```

```{r}
meta1
```
## Forest
```{r}

forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or repair", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Replacement",
       col.label.right    = "darkred")

```

## Export
```{r}
png(filename = "5.png", 
    type = "cairo",
    units = "in", 
    width = 10, 
    height = 5, 
    pointsize = 12, 
    res = 96)



forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or repair", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Replacement",
       col.label.right    = "darkred")

dev.off()

```

-------------------------------------------------------------------------------

# 6. Replacement TS (5)
## Data selection
```{r}
data_meta <- df %>% 
  filter(groups == "Replacement TS")
data_meta
```
```{r}
meta1 <- metabin(EvA, TotalA, 
                 EvB, TotalB, 
                 data = data_meta,  
                 sm = "OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = paste(firstAuthor, year, intervention_a))

```


## Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE, 
            cex.studlab = .55)
```


## Heterogeneity

```{r}

baujat.meta(meta1, 
            yscale = 10, xmin = 3, ymin = 10, 
            cex.studlab = .50)
```


## Meta-analysis and forest plot
```{r}
summary(meta1)
```

```{r}
meta1
```
## Forest
```{r}

forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or repair", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Replacement",
       col.label.right    = "darkred")

```


## Export
```{r}
png(filename = "6.png", 
    type = "cairo",
    units = "in", 
    width = 10, 
    height = 5, 
    pointsize = 12, 
    res = 96)


forest.meta(meta1,  
       comb.fixed = FALSE,
       sortvar = year, 
       # LEFT
       label.left         = "Seal or repair", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Replacement",
       col.label.right    = "darkred")


dev.off()

```


-------------------------------------------------------------------------------




# Citations

```{r}
citation()
citation(package = "tidyverse")
citation(package = "meta")

```